---
title: "Day 8 Activities - Data Viz"
author: "Colleen McCamy"
date: "2022-08-17"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}

library(tidyverse)
library(here)
library(janitor)
library(lubridate)
library(grid)

#library(patchwork)
library(ggrepel)
library(gghighlight)
library(paletteer)
#library(ggExtra)
#library(ggbeeswarm)
#library(gapminder)
#library(forcats)
#library(sf)

```


Reading in data

```{r}

space_launches <- read_csv(here::here("data", "space_launches.csv"))

launch_date <- space_launches |> 
  filter(str_detect(type, pattern = "Thor Delta"))

```

create your worst possible graph by customizing (from the ggplot default) in at least 8 ways - more encouraged - to make it as terrible as possible

```{r}

img <- jpeg::readJPEG(here("Chris_Hemsworth_as_Thor.jpeg"))

my_great_graph <- ggplot(data = launch_date, aes(x = mission, y = type)) +
  scale_fill_continuous(guide = FALSE) +
  annotation_custom(rasterGrob(img, 
                               width = unit(1,"npc"), 
                               height = unit(1,"npc")), 
                    -Inf, Inf, -Inf, Inf) +
  geom_jitter(fill = "#FF00F3", color = "#8AAE98") +
   theme(panel.grid.major.x = element_line(color = "#6C1A09"),
        panel.grid.minor.y = element_line(color = "#E6F407"), 
        axis.title = element_text(color = "#68F1F1", size = 25),
        axis.text.y = element_text(color = "#33FF84"),
        text = element_text(size = 18, family="Comic Sans MS"),
        panel.background = element_rect(fill = "#8A637A")) +
  labs(y = "Thor", x = "Mission", title = "Types and Mission",
        caption = "image not copywritten")

my_great_graph

ggsave(here::here("plots", "thor_plot.png"))

class(launch_date$launch_date)

launch_years <- launch_date |> 
  mutate(launch_date = lubridate::dmy(launch_date)) |> 
  mutate(year = year(launch_date))


```


```{r}

sf_emissions <- read_csv(here("data", "San_Francisco_Communitywide_Greenhouse_Gas_Inventory.csv"))

```


Create a summary table of total annual greenhouse gas emissions (only from Emissions_mtCO2e column) by sector_general

```{r}

sf_emissions_sum <- sf_emissions |> 
  group_by(Sector_General) |> 
  summarize(sum(Emissions_mtCO2e, na.rm = TRUE))

```


Create a summary table of total annual greenhouse gas emissions (only from Emissions_mtCO2e column) by year and commodity type

```{r}

sf_year_com <- sf_emissions |> 
  group_by(Calendar_Year, Commodity_Type) |> 
  summarize(emissions = sum(Emissions_mtCO2e, na.rm = TRUE))

```


Create a subset of the data that only contains observations from 2005 on, only for observations where Sector_Detail2 contains the pattern “PG&E”, then limit to columns Calendar_Year, Sector_Detail2 and Emissions_mtCO2e.

```{r}



```

